\subsection{Defining Tasks over Open Worlds}

We will now leverage the expressive power of the abstractions introduced in Section \ref{abstractions} to specify robot tasks over open worlds. We revisit Example \ref{Ex:mailbot1} and make use of the open world abstractions. For illustration purposes, we use Structured English as the specification language $\Lambda$.

\begin{myExample}\label{Ex:mailbot2} Autonomous Mailbot (revisited)\\
\texttt{Group Letters is letter1, letter2}\\
\texttt{Group Offices is office1, office2}\\
\texttt{Letters correspond to Offices}\\
\texttt{if you are sensing any Letter then do PickUp and go to corresponding Office}\\ 
where \texttt{Letters} and \texttt{Offices} are groups of environment and robot (region) propositions, respectively. Notice how the sentence describing the task (lines 4-5) does not refer to any specific letters (\texttt{letter1}, \texttt{letter2}) or offices (\texttt{office1}, \texttt{office2}). In fact, even if the group \texttt{Letters} was empty (\texttt{Group Letters is empty}), the user would still be able to specify the mission above.
\end{myExample}

If a new letter is received, .i.e., sensed by a ``new letter sensor" $d_{m} \in \mathcal{D}$, a new proposition, $\pi_{mt} = $\texttt{letterNew}, would be added to $AP_t$. There are two requirements for the mission in Example \ref{Ex:mailbot2} to reflect the addition of the new proposition. First, \texttt{letterNew} has to be added to the group \texttt{Letters}, not just the set $AP_t$. Second, an office proposition, e.g. \texttt{officeNewLetter}, has to be created, if necessary, and added to the group \texttt{Offices}, in order to maintain the correspondence between \texttt{Letters} and \texttt{Offices}. The two requirements define a subproblem of Problem \ref{Prob:newSpec}:

\begin{myProblem}\label{Prob:correspondence}
	\textbf{(New Propositions and Correspondence):} Given a mission specification $\mathcal{M}_k$, and a new proposition $\pi_{mt} = D(m, t)$, define a mechanism for (i) adding $\pi_{mt}$ to a group of propositions $G_m$ in $\mathcal{M}$, and (ii) creating additional propositions, if necessary, and adding them to the corresponding groups $C(G_m)$.
\end{myProblem}

\subsection{Rewriting the Specification} % Re-synthesis (not local yet)

To address Problem \ref{Prob:correspondence}, we introduce another element to the specification language $\Lambda$, the ``add to Group" operator.

\begin{myDefinition}\label{Def:addto}
	\textbf{(add to Group):} When used in a sentence of $\mathcal{M} \in \Lambda$, the \emph{add to Group} operator takes the new proposition $\pi_{mt} = D(m,t)$, by reading the sensor preceding the operator, and adds it to its argument, a group of propositions $G_m$. 
	Furthermore, it creates additional propositions $\mathcal{C}(\pi_{mt})$, and adds them to the corresponding groups $\mathcal{C}(G_m)$. 
	
	More concisely:
	\begin{equation}
	\begin{split}
		\X d_m \Leftrightarrow &((G_m = G_m \cup \left\{ \pi_{mt} \right\}) \\
		\bigwedge_{G_i \in \mathcal{C}(G_m)} &(G_i = G_i \cup \left\{ \mathcal{C}(\pi_{mt}) \right\}))
	\end{split}
	\end{equation}
\end{myDefinition}
In Structured English, it would be used as follows: \texttt{if you are sensing somethingNew then add to GroupName}, where \texttt{somethingNew} $\in \mathcal{D}$. The new propositions are named either by a predefined naming scheme, by prompting the human user, or using information from the low-level sensor abstracted by $d_m \in \mathcal{D}$.

Since we are now adding propositions besides those added by the detection sensors $d_m \in \mathcal{D}$, as a direct result of the world being open, we have to restate Definition \ref{Def:openworld} as follows:

\begin{myDefinition}\label{Def:openworld2}	
	\textbf{(Open World Model -- revisited):} Our model $\W = \left\{ AP_0, AP_1, \ldots, AP_k \right\}$ is now updated such that the propositions added in order to maintain correspondence are also added to the set of atomic propositions. That is, 
	\begin{equation}\label{Eq:updateAP2}
		AP_{t+1} = AP_t \bigcup_{m=1}^{M}D(m, t) \bigcup_{m=1}^{M}\mathcal{C}(D(m, t)),
	\end{equation}
	replaces Eq. \eqref{Eq:updateAP}. Eq. \eqref{Eq:updateW} remains the same.
\end{myDefinition}

\begin{myAssumption}
	The grounding \cite{Grounding2013} of new propositions 
%	$\left\{ \pi_{mt}, \mathcal{C}(\pi_{mt}) \right\}$ 
$\pi \in AP_{k+1} \backslash AP_k$ to the robot's physical world is either obtained from the robot's low-level sensors $d \in \mathcal{D}$, or by prompting the human user.
Some auxiliary propositions, such as robot memory propositions, do not require grounding to the physical world.
%	The correspondence, i,e., the relationship of new elements of the open world to the robot's mission, is provided either by the robot's low-level sensors, or by prompting the human user. That is, for a proposition $\pi_{mk} = A(m, k)$, added to a group of propositions, the semantics of additional propositions $C(\pi_{mk})$ can be inferred.
	% Rephrase when Problem 2 is stated. Remember, you can use Groups now!
\end{myAssumption}

For instance, in Example \ref{Ex:mailbot2}, a new letter would result in new propositions, e.g. \texttt{letterNew} and\texttt{officeNew}. The sensor proposition \texttt{letterNew} would be grounded to the recipient's name on the letter. The information for grounding \texttt{officeNew} to a location on the robot's workspace can be inferred from the letter itself (address field), which the robot can look up in a digital map. If the new office is not part of the current map, the robot could prompt the user for its location, and then add it to its discrete abstraction of the workspace.

All the specification rewriting described so far has resulted in mission specification $\mathcal{M}_{k+1}$ that can be parsed to an LTL specification $\varphi [k+1]$, according to Eq. \eqref{Eq:newSpec}. However, for the updates to be reflected in the robot's discrete strategy, $\varphi [k+1]$ has to be passed to the synthesis algorithm in order to extract a new winning strategy. This process is dubbed ``re-synthesis" \cite{BingxinRSS2012}. We associate a robot proposition, e.g. \texttt{resynthesis}, with it. For example, in the setting of Example \ref{Ex:mailbot2}, and using Structured English, we could say:
\texttt{if you are sensing newLetter then add to Letters and do resynthesis}. 

Notice that the user chooses when re-synthesis will take place. Given the task above, the robot would update its strategy immediately after detecting a letter for a new recipient. In a search and rescue setting, it would make more sense for the robot to finish executing other actions before re-synthesizing.

\begin{myExample}\label{Ex:SnS} Search and Rescue Specification (partial)\\
	\texttt{Group Regions is \ldots}\\
	\texttt{visit each Region if and only if you are not activating rescueSurvivor}\\
	\texttt{if you are sensing newRegion then add to Regions and do needToResynthesize}\\
	\texttt{do resynthesis if and only if you are not activating rescueSurvivor and you are activating needToResynthesize}\\
	where \texttt{needToResynthesize} is a robot memory proposition that enables the robot to remember it detected a new region and that is has to re-synthesize eventually.
\end{myExample}

The definition of the \emph{add to Group} operator and \emph{resynthesis} conclude the augmentation of the specification language $\Lambda$.

% Stuff on initial conditions, goal reordering?

%
%Finally, we set the index $k$ (Definitions \ref{Def:openworld}, \ref{Def:openworld2} to also be incremented when re-synthesis takes place:
%	\begin{equation*}
%		k \leftarrow 
%		\begin{cases}
%			k + 1, & \text{if } \bigvee_{m=1}^{M} x_{d_m} \vee y_{\texttt{resynthesize}} \\
%			k, & \text{otherwise}
%		\end{cases}
%	\end{equation*}

%\subsection{Exploring the Physical Workspace}
%
%So far we have not made a distinction among the different types of propositions that are added to $AP_k$; environment, action, and region propositions. \ldots
%
%\textbf{Is there a distinction after all?}
%
%BFS/DFS \ldots

%In the robotics domain, more often than not, the state-space has a physical subset: the workspace that the robot operates in. When defining tasks using the open world abstractions that were introduced in Section \ref{abstractions}, one needs to account for the fact that the robot could simply restrict itself to its current workspace, never discovering new regions, without violating the specification. Therefore, part of the specification has to direct the robot to expand its physical workspace, and incorporate newly discovered regions to the discrete abstraction and mission specification.

%\begin{myAssumption}
%	New regions are discovered when the robot visits an adjacent region. The structure of the new region becomes known to the robot at that time instant. In the future, we will remove this assumption and add a mapping aspect. \ldots
%\end{myAssumption}
%
%To this end, we dedicate a portion of the mission specification to this ``exploration sub-task". It is worth noting that (i) the approach is still valid in the case that the robot already has full knowledge of its workspace, and (ii) that, since exploration is part of the specification, the user can define how the robot will deal with the open world, and under which conditions it will perform actions such as exploration or re-synthesis. The statements in this sub-task are instructions on how the robot should visit newly discovered regions.
%
%Putting everything together, we create the following template for defining specifications that have mixed mission and exploration tasks. Specifically, the specification is broken into three parts. The first part is the actual mission specification and its content does not depend on whether the robot is operating in an open world. The last part is the exploration sub-task mentioned above, and is the same for all scenarios involving exploration of the physical workspace. Therefore, it can be automatically generated, and appended to any specification. In the intermediate part, dubbed ``exploration settings", the user creates a link between the mission and exploration tasks. On one end of the spectrum, the user may choose to have the robot always be in exploration mode (e.g. \texttt{always do exploreMODE}). On the other end, the user may decide to ignore the open world aspect of the problem and restrict the mission to the currently known state-space. In between the two extremes, the user can set conditions for when the robot is allowed to explore. For example, in a search and rescue scenario, it would be sensible for the exploration settings to include the following constraint: \texttt{do exploreMODE if and only if you are not activating rescuingSurvivor}. This would prevent the robot from exploring a disaster area while attempting to help a survivor and guide him to a safe location. Note that \texttt{exploreMODE} is just a name for a binary robot proposition. Finally, the exploration settings also contain instructions for adding non-region propositions, such as new sensors and actions, to their corresponding groups.

%\begin{algorithm}
%	\textbf{Exploration sub-task:}\\
%	{\small
%	\texttt{...}
%	}
%\end{algorithm}

% END